\textsf{Are large language models superhuman chemists?}

### 2024-03-25 src/tex/appendix.tex
feat: first addition of chemical analysis
co-authored-by: Adrian Mirza <adrianmirza81@gmail.com>

>>>>

\subsubsection{Model performance as a function of molecular structure}

\begin{figure}
    \centering
    \includegraphics{figures/correlation_is_number_nmr_peaks_num_atoms.pdf}
    \caption{\textbf{Model performance as a function of molecular structure.} The violinplots show the distribution of the number of atoms in the molecules for questions that were answered completely correctly and those that were not. We do not observe a clear correlation between the number of atoms in the molecules and the performance of the models. }
    \script{correlate_with_molecule_features.py}
    \label{fig:molecular_structure_vs_model_performance}
\end{figure}
